\bf Visual Inference for Significance and Goodness-of-Fit Testing for a Social Network Model

### 2017-10-31 ASApaper/paper-child.Rnw

\hh{this is the power of the visual test XXX}
We futher explore this relationship between identification of the alternative data in the lineup and the parameter, effect size, and lineuptype with a generalized linear mixed model \st{that provides us with an estimate of the power of the visual test.} The response variable, $Y_{i\ell m}$, is binary, indicating whether participant $m$ picked the alternative data plot in lineup $\ell$. The covariate $x_{\ell 1}$ takes on the value -1 or 1 according to the lineup type code in Table~\ref{tab:experdetail}. In most cases, -1 indicates the parameter value is less than original estimate, while 1 indicates the parameter value is at or above the original estimate. The continuous covariate $x_{\ell 2}$ is the centered and scaled size of the effect of interest from which the alternative data were simulated, the values of which are labeled ``easy", ``medium", and ``hard" in Table~\ref{tab:experdetail} according to how difficult we thought the Turk participants would find each lineup. In Equation~\ref{eq:glmm}, $i \in \{1, 2, 3, 4, 5\}$ corresponding to the effects $\beta_3, \beta_4, \beta_2, \beta_6, \beta_5$, respectively. We include random effects in the model for each lineup, $\delta_{\ell}$ and each participant, $\epsilon_m$, and fit a hierarchical model as follows:
\begin{align}
\begin{split}
Y_{i\ell m} &\sim \text{Bernoulli}(\pi_{i\ell m}) \\
\text{logit}(\pi_{i\ell m}) & = \mu + \alpha_{i} + \theta\mathbb{I}(x_{\ell 1} = 1) + \gamma x_{\ell 2} + \\ & (\alpha\theta)_i \mathbb{I}(x_{\ell 1} = 1) + (\alpha\gamma)_i x_{\ell 2} + (\theta\gamma)\mathbb{I}(x_{\ell 1} = 1)x_{\ell 2} + \\ & (\alpha\theta\gamma)_i\mathbb{I}(x_{\ell 1} = 1) x_{\ell 2} + \delta_{\ell} + \epsilon_{m} \label{eq:glmm} \\
\delta_{\ell} & \sim N(0, \sigma^2_{\delta}) \\
\epsilon_{m} & \sim N(0, \sigma^2_{\epsilon})
\end{split}
\end{align}
The results of fitting this model using \texttt{glmer} from the \texttt{lme4} package are summarized in Table~\ref{tab:glmmests} \citep{lme4}. The baseline condition for this model against which all other experimental conditions are compared is the first condition in Table~\ref{tab:experdetail}, for parameter $\beta_1$ and lineup type -1. The expected value of the link function for this scenario with $\beta_1 = 0$ is $\mu$, and the expected probability that a new observer will pick out the data plot in a new lineup generated from this scenario is $\frac{\exp(\mu)}{1+\exp{\mu}}$. Similarly, for a new lineup generated from the tenth condition in in Table~\ref{tab:experdetail}, with $\beta_6 = 1$, and lineup type 1, the expected value of the link function is $\mu + \alpha_{4} + \theta + \gamma + (\alpha\theta)_4 + (\alpha\gamma)_4  + (\theta\gamma) + (\alpha\theta\gamma)_4$. The corresponding expected probability that a new observer viewing a new lineup from this scenario is: 
\begin{equation}
\frac{\exp\{\mu + \alpha_{4} + \theta + \gamma + (\alpha\theta)_4 + (\alpha\gamma)_4  + (\theta\gamma) + (\alpha\theta\gamma)_4\}}{1 + \exp\{\mu + \alpha_{4} + \theta + \gamma + (\alpha\theta)_4 + (\alpha\gamma)_4  + (\theta\gamma) + (\alpha\theta\gamma)_4\}}
\end{equation}

>>>>

We futther explore this relationship between identification of the alternative data in the lineup and the parameter, effect size, and lineup type with a generalized linear mixed model that provides us with an estimate of the power of the visual test. The response variable, $Y_{i\ell m}$, is binary, indicating whether participant $m$ picked the alternative data plot in lineup $\ell$ for effect $i$. The covariate $x_{\ell 1}$ takes on the value -1 or 1 according to the lineup type code in Table~\ref{tab:experdetail}. In most cases, -1 indicates the parameter value is less than original estimate, while 1 indicates the parameter value is at or above the original estimate. The continuous covariate $x_{\ell 2}$ is the centered and scaled size of the effect of interest from which the alternative data were simulated, the values of which are labeled ``easy", ``medium", and ``hard" in Table~\ref{tab:experdetail} according to how difficult we thought the Turk participants would find each lineup. In Equation~\ref{eq:glmm}, $i \in \{1, 2, 3, 4, 5\}$ corresponding to the effects $\beta_3, \beta_4, \beta_2, \beta_6, \beta_5$, respectively. We include random effects in the model for each lineup, $\delta_{\ell}$ and each participant, $\epsilon_m$, and fit a hierarchical model as follows:

\begin{align}
\begin{split}
Y_{\ell m} &\sim \text{Bernoulli}(\pi_{\ell m}) \\
\text{logit}(\pi_{\ell m}) & = \alpha_{\ell} + \beta_{\ell} x + \delta_{\ell} + \epsilon_{m} \label{eq:glmm} \\
\delta_{\ell} & \sim N(0, \sigma^2_{\delta}) \\
\epsilon_{m} & \sim N(0, \sigma^2_{\epsilon})
\end{split}
\end{align}

\hh{
$\ell$ encompasses all 12 combinations of parameter and positive/negative direction of the effect size.
}

\begin{align}
\begin{split}
Y_{i\ell m} &\sim \text{Bernoulli}(\pi_{i\ell m}) \\
\text{logit}(\pi_{i\ell m}) & = \mu + \alpha_{i} + \theta\mathbb{I}(x_{\ell 1} = 1) + \gamma x_{\ell 2} + \\ & (\alpha\theta)_i \mathbb{I}(x_{\ell 1} = 1) + (\alpha\gamma)_i x_{\ell 2} + (\theta\gamma)\mathbb{I}(x_{\ell 1} = 1)x_{\ell 2} + \\ & (\alpha\theta\gamma)_i\mathbb{I}(x_{\ell 1} = 1) x_{\ell 2} + \delta_{\ell} + \epsilon_{m} \label{eq:glmm} \\
\delta_{\ell} & \sim N(0, \sigma^2_{\delta}) \\
\epsilon_{m} & \sim N(0, \sigma^2_{\epsilon})
\end{split}
\end{align}

\hh{XXX define all of the parameters above XXX}

The results of fitting this model using \texttt{glmer} from the \texttt{lme4} package are summarized in Table~\ref{tab:glmmests} \citep{lme4}. The baseline condition for this model against which all other experimental conditions are compared is the first condition in Table~\ref{tab:experdetail}, for parameter $\beta_1$ and lineup type -1. The expected value of the link function for this scenario with $\beta_1 = 0$ is $\mu$, and the expected probability that a new observer will pick out the data plot in a new lineup generated from this scenario is $\frac{\exp(\mu)}{1+\exp{\mu}}$. Similarly, for a new lineup generated from the tenth condition in in Table~\ref{tab:experdetail}, with $\beta_6 = 1$, and lineup type 1, the expected value of the link function is $\mu + \alpha_{4} + \theta + \gamma + (\alpha\theta)_4 + (\alpha\gamma)_4  + (\theta\gamma) + (\alpha\theta\gamma)_4$. The corresponding expected probability that a new observer viewing a new lineup from this scenario is: 
\begin{equation}
\frac{\exp\{\mu + \alpha_{4} + \theta + \gamma + (\alpha\theta)_4 + (\alpha\gamma)_4  + (\theta\gamma) + (\alpha\theta\gamma)_4\}}{1 + \exp\{\mu + \alpha_{4} + \theta + \gamma + (\alpha\theta)_4 + (\alpha\gamma)_4  + (\theta\gamma) + (\alpha\theta\gamma)_4\}}
\end{equation}
